---
title: "GXT and CVD; initial results"
author: "Byron C Jaeger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
---

```{r setup, include=FALSE}

# set options for the report
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

## target knits Rmds in their own session, so load libraries here.
source("packages.R")

rspec <- round_spec() |> 
  round_using_decimal(digits = 2)

tar_load(data_excluded)
tar_load(tbl_fit_death)
tar_load(tbl_fit_cvd)
tar_load(tbl_chrs)

drop_na_rows <- function(x){
  keep_rows <- apply(x, 1, function(.x) !all(is.na(.x)))
  return(x[keep_rows, ])
} 

```

\newpage

__Table__ Inclusion criteria for the current study

__Question__: Should we drop the last exclusion given our focus is on all cause mortality?

```{r}
flextable(data_excluded$table) |> 
 width(j = 1, width = 4) |> 
 set_header_labels(name = 'Exclusion criteria', 
                   value = 'Number of participants')
```

\newpage 

__Table__ Participant characteristics at the Year 0 Exam.

```{r}

tbl_chrs$Y0 |> 
 as_flex_table() |> 
 theme_box() |> 
 align(align = 'center', part = 'all') |> 
 align(j = 1, align = 'left', part = 'all')
  
```

\newpage 

__Table__ Participant characteristics at the Year 20 Exam.

```{r}

tbl_chrs$Y20 |> 
 as_flex_table() |> 
 theme_box() |> 
 align(align = 'center', part = 'all') |> 
 align(j = 1, align = 'left', part = 'all')
  
```

\newpage 

__Table__: Hazard ratio (95%) for all-cause mortality among CARDIA participants in the current analysis.

```{r tbls_death}


tbl_fit_death |> 
 mutate(
  level = recode(
   level,
   "gteq 12 minutes" = "\u2265 12 minutes",
   "8 to 12 minutes" = "\u2265 8 to < 12 minutes",
   "lt 8 minutes" = "< 8 minutes",
   "lt 25% decline" = "< 25% decline",
   "25 to 35% decline" = "\u2265 25% to < 35% decline",
   "gteq 35% decline" = "\u2265 35% decline"
  )
 ) |> 
 mutate(
  tbl_value = if_else(
   is.na(est),
   true = '1 (ref)',
   false = table_glue("{est}\n({lwr}, {upr})", rspec = rspec)
  ),
  .after = level
 ) |>
 mutate(across(starts_with('pval'), table_pvalue)) |> 
 select(-est, -lwr, -upr) |> 
 pivot_wider(names_from = model, values_from = contains('val')) |> 
 select(variable, level,
        tbl_value_m1,
        tbl_value_m2,
        tbl_value_m3,
        pval_race_m3,
        pval_sex_m3) |> 
 as_grouped_data(groups = 'variable') |> 
 as_flextable(hide_grouplabel = TRUE) |> 
 set_header_labels(
  level = 'Characteristic',
  tbl_value_m1 = "Model 1",
  tbl_value_m2 = "Model 2",
  tbl_value_m3 = "Model 3",
  pval_race_m3 = "Race",
  pval_sex_m3 = "Sex"
 ) |> 
 add_header_row(values = c("", 
                           "Hazard ratio (95% CI)", 
                           "P-value\nfor interaction"), 
                colwidths = c(1, 3, 2)) |> 
 theme_box() |> 
 width(j = ~ pval_race_m3 + pval_sex_m3, 
       width = 2/3) |> 
 width(j = ~ tbl_value_m1 + tbl_value_m2 + tbl_value_m3, 
       width = 1) |>   
 width(j = ~ level, width = 1.75) |> 
 italic(i = ~!is.na(variable), italic = TRUE) |> 
 align(align = 'center', part = 'all') |> 
 align(j = 1, align = 'left', part = 'all')

```

\newpage 

# Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>
